The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
cite PUM paper
add Matrix-free operators subsection; mark a couple to be written

\subsection{The \texttt{FE\_Series} namespace?}

@@

The original \texttt{\dealii{}} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on specific
features of the library, please consider citing any of the following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$ adaptivity: \cite{BangerthKayserHerold2007};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16}.
\end{itemize}

>>>>

TODO: Denis

\subsection{The \texttt{FE\_Series} namespace}

TODO: Denis

\subsection{Matrix-free operators}

Facilitate the usage of matrix-free method by providing a \verb!MatrixFreeOperator::Base! class,
which implements various interface to matrix-vector products, including necessary operations when used in
the context of the geometric multigrids, methods needed for usage within the linear operator as well as with Jacobi preconditioner. 
The derived classes only need to implement \verb!apply_add()! method that is
used in the \verb!vmult()! functions, and a method to compute the diagonal entries of the underlying matrix. 
The \verb!MatrixFreeOperator! namespace contains implementations of \verb!MatrixFreeOperators::LaplaceOperator! and 
\verb!MatrixFreeOperators::MassOperator!.

TODO: Mention updated Step-37.

@@

The original \texttt{\dealii{}} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on specific
features of the library, please consider citing any of the following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$ adaptivity: \cite{BangerthKayserHerold2007};
  \item For $PUM$ and enrichment of the FE space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16}.
\end{itemize}
